Naturalness in U(1) extensions of the MSSM

### 2014-12-19 paper/e6ssm-tuning-paper.tex
started writing conclusions badly.  may change whole thing...

A number of alternative measures have also been applied in the
literature \cite{Anderson:1994dz, Anderson:1994tr,
  Anderson:1995cp,Anderson:1996ew,Ciafaloni:1996zh,Chan:1997bi,
  Barbieri:1998uv,
  Giusti:1998gz,Casas:2003jx,Casas:2004uu,Casas:2004gh,Casas:2006bd,Kitano:2005wc,
  Athron:2007ry, Athron:2007qr, Baer:2012up} with varying motivations.
A very different approach is to work within a Bayesian analysis.
There the concept of naturalness is automatically incorporated since
in models where one must fine tune parameters to fit measured values
of the observables, the region with high likelihood will occupy a tiny
prior volume \cite{Allanach:2007qk, Cabrera:2008tj, Ghilencea:2012gz,
  Ghilencea:2012qk, Fichet:2012sn, Kim:2013uxa} suppressing the
posterior.  Indeed in the MSSM and NMSSM if one transforms GUT scale
parameters to the VEVs, the inverse of the Jacobian for this
transformation looks quite like the derivatives that appear in the
traditional fine tuning measure \cite{Allanach:2007qk, Cabrera:2008tj,
  Kim:2013uxa}.  If one thinks more generally then a model without
fine tuning is one where the parametrisation is such that all the
parameters are observables \cite{Fichet:2012sn, Kim:2013uxa}.  This
provides a quite general definition of fine tuning as $1/|J|$ where
$|J|$ is the determinant of the Jacobian for the co-ordinate
transformation between the parameters and the
observables. Interestingly this means the tuning is the ratio of the
infinitesimal observable space space volume element to the
infinitesimal parameter space element and coincides with the measure
proposed in \cite{Athron:2007ry} when the interval of variation is
taken to zero.

@@

\section{\label{sec:conclusion}Conclusions}

>>>>

A number of alternative measures have also been applied in the
literature \cite{Anderson:1994dz, Anderson:1994tr, Anderson:1995cp,
  Anderson:1996ew, Ciafaloni:1996zh, Chan:1997bi, Barbieri:1998uv,
  Giusti:1998gz, Casas:2003jx, Casas:2004uu, Casas:2004gh,
  Casas:2006bd, Kitano:2005wc, Athron:2007ry, Athron:2007qr,
  Baer:2012up} with varying motivations.  A very different approach is
to work within a Bayesian analysis.  There the concept of naturalness
is automatically incorporated since in models where one must fine tune
parameters to fit measured values of the observables, the region with
high likelihood will occupy a tiny prior volume \cite{Allanach:2007qk,
  Cabrera:2008tj, Ghilencea:2012gz, Ghilencea:2012qk, Fichet:2012sn,
  Kim:2013uxa} suppressing the posterior.  Indeed in the MSSM and
NMSSM if one transforms GUT scale parameters to the VEVs, the inverse
of the Jacobian for this transformation looks quite like the
derivatives that appear in the traditional fine tuning measure
\cite{Allanach:2007qk, Cabrera:2008tj, Kim:2013uxa}.  If one thinks
more generally then a model without fine tuning is one where the
parametrisation is such that all the parameters are observables
\cite{Fichet:2012sn, Kim:2013uxa}.  This provides a quite general
definition of fine tuning as $1/|J|$ where $|J|$ is the determinant of
the Jacobian for the co-ordinate transformation between the parameters
and the observables. Interestingly this means the tuning is the ratio
of the infinitesimal observable space space volume element to the
infinitesimal parameter space element and coincides with the measure
proposed in \cite{Athron:2007ry} when the interval of variation is
taken to zero.

@@

\section{\label{sec:conclusion}Conclusions}
Prior to stringent experimental constraints on the mass of the
lightest Higgs boson and squarks in supersymmetric models, a simple
picture of a natural SUSY model emerged from theoretcal reasoning,
with soft masses set to similar values at the GUT scale through local
gravity interactions with the hidden sector.  Through the use of
renormalisation group running one can then see that at the EW scale
the stops and soft Higgs masses (which appear directly in the EWSB
conditions) should appear in the the EWSB condition for $M_Z$ and
therefore it was expected that these masses should not be much bigger
than $100$ GeV.  However to disturb this elegant picture first LEP
placed constraints on the Higgs mass, requiring it to be above 114.4
GeV \cite{}, which already introduced significant tuning for
constrained models, and then the LHC meaured the Higgs to be around
$125$ GeV.

However
